\chapter{Why choose Kubernetes over Docker Swarm}

\paragraph{\hspace{24pt}}
The major question is why should we use Kubernetes instead of Docker Swarm? What good will it do? The following points will compare both the technologies and answer the above questions.

\paragraph{\hspace{24pt}}
Kubernetes is a much more powerful tool than Docker Swarm. It can handle containers and offer immense scalability and automation at the same time. This means it possesses greater efficiency than the Docker Swarm.

\paragraph{\hspace{24pt}}
Kubernetes has an in-built library and process for monitoring and logging, which lacks in the Docker Swarm. Hence, the Docker Swarm has to use third party applications to these features.

\paragraph{\hspace{24pt}}
Kubernetes overcomes the constraints of Docker and Docker API.

\paragraph{\hspace{24pt}}
It is more widely deployed than Docker Swarm.

\paragraph{\hspace{24pt}}
If a node fails, it is replaced so fast that you don’t even come to know a node has failed unless you do a detailed troubleshoot on it.

\paragraph{\hspace{24pt}}
Since we all seek after efficiency and accuracy, Kubernetes is a much better choice than Docker Swarm in almost all aspects.

\paragraph{\hspace{24pt}}
The performance of Kubernetes surpasses that of the Docker Swarm.

\paragraph{\hspace{24pt}}
However, there is one drawback of Kubernetes, i.e., the installation process. It is complex and time consuming. But, if the end result is so spectacular, such a drawback can be neglected.