\chapter{Using Kubernetes Instead of Docker Swarm}

\begin{itemize}
    \item The efficiency of the afore mentioned model can be increased by the utilization of Kubernetes rather than Docker Swarm.
    \item When we compare the two container clustering tools, namely Kubernetes and Docker, Kubernetes excel in both power as well as performance. It also enables greater flexibility in container management.
    \item Like Docker, Kubernetes is also an open- source system that provides similar functions such as automating deployment, scaling, and the management of containerized applications.
    \item Therefore, we can use Kubernetes for optimizing the existing design to make it more efficient. It also provides fault tolerance.
\end{itemize}

\section{Characteristics of Kubernetes}
\begin{itemize}
    \item Planet Scale
    \item Never Outgrow
    \item Run Anywhere
\end{itemize}

\section{Features of Kubernetes}
\begin{itemize}
    \item Automatic Binpacking
    \item Self-Healing
    \item Horizontal Scaling
    \item Storage Orchestration
    \item Batch Execution
    \item Automated Rollouts and RollBacks
    \item Service Discovery and Load Balancing
    \item Secret and Configuration Management
\end{itemize}

\section{Why Kubernetes instead of Docker Swarm?}

\paragraph{\hspace{24pt}}
The major question is why should we use Kubernetes instead of Docker Swarm? What good will it do? The following points will compare both the technologies and answer the above questions.

\paragraph{\hspace{24pt}}
Kubernetes is a much more powerful tool than Docker Swarm. It can handle containers and offer immense scalability and automation at the same time. This means it possesses greater efficiency than the Docker Swarm.

\paragraph{\hspace{24pt}}
Kubernetes has an in-built library and process for monitoring and logging, which lacks in the Docker Swarm. Hence, the Docker Swarm has to use third party applications to these features.

\paragraph{\hspace{24pt}}
Kubernetes overcomes the constraints of Docker and Docker API.

\paragraph{\hspace{24pt}}
It is more widely deployed than Docker Swarm.

\paragraph{\hspace{24pt}}
If a node fails, it is replaced so fast that you don’t even come to know a node has failed unless you do a detailed troubleshoot on it.

\paragraph{\hspace{24pt}}
Since we all seek after efficiency and accuracy, Kubernetes is a much better choice than Docker Swarm in almost all aspects.

\paragraph{\hspace{24pt}}
The performance of Kubernetes surpasses that of the Docker Swarm.

\paragraph{\hspace{24pt}}
However, there is one drawback of Kubernetes, i.e., the installation process. It is complex and time consuming. But, if the end result is so spectacular, such a drawback can be neglected.